---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# dev_r_shiny_env_example

Before building a Dockerfile, the system requirements and all packages used in your projects must be defined in the Dockerfile. In this example, I defined a long list of the system requirements because of renv.lock file. Please, check requirements of the R packages you used on [Posit Package Manager](https://packagemanager.posit.co/client/#/). 

First, build the Dockerfile for R Shiny Environment
```{bash eval=FALSE, include=TRUE}
docker build -t example/dev_r_shiny_env .
```

Go to App folder then build the Dockerfile for App
```{bash eval=FALSE, include=TRUE}
docker build -t example/shiny_app .
```

Run the app in production
```{bash eval=FALSE, include=TRUE}
docker run -d -p 3838:3838 example/shiny_app
```

In order to create renv.lock file properly,
```{r eval=FALSE, include=TRUE}
options(renv.config.auto.snapshot = T)
renv::settings$snapshot.type("all")
renv::snapshot()
```

